Simulation Study of Angular Resolution of a New Electromagnetic Sampling Calorimeter

### 2022-05-31 paper.tex
updates

Figure~\ref{fig:angle_reco_dep_gr} (a) shows the angular resolution as a function of the incident photon energy ($E_{\gamma}$) at $\theta=$~10$^{\circ}$. Angular resolutions are fitted with a function of $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(GeV)}$, where $p_{0}$ represents an energy-independent contribution and is estimated to be 0.43~$\pm$~0.01$^{\circ}$, and $p_{1}$ denotes the energy-dependent parameter, mainly related with the development of the EM shower. $p_{1}$ is estimated to be gradually decreasing from 1.28$^{\circ}$ to 1.04$^{\circ}$ with increasing incidence angles as shown in Fig.~\ref{fig:angle_reco_dep_gr} (b).

>>>>

Figure~\ref{fig:angle_reco_dep_gr} (a) shows the angular resolution as a function of the incident photon energy ($E_{\gamma}$) at $\theta=$~25$^{\circ}$. Angular resolutions are fitted with a function of $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(GeV)}$, where $p_{0}$ and $p_{1}$ represent an energy-independent and energy-dependent contribution, respectively. $p_{0}$ and $p_{1}$ are constant for $\theta>$~10$^{\circ}$ and estimated to be 0.29$^{\circ}$ and 1.24$^{\circ}$, respectively. For small $\theta$, The values are deviating up to $\pm$0.15$^{\circ}$  as shown in Fig.~\ref{fig:angle_reco_dep_gr} (b).
